---
title: "Test Results"
author: "Matthew Goodsell"
date: "6/22/2020"
output: 
  html_document:
   keep_md: TRUE 
---

```{r packages & loading data, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# loading package
pacman::p_load(tidyverse, DT)

# loading in data of original test
test_0.09 <- read_csv("New_modified_TestResults_circle_rad_0.09.csv")
test_0.1 <- read_csv("New_modified_TestResults_circle_rad_0.1.csv")
test_0.11 <- read_csv("New_modified_TestResults_circle_rad_0.11.csv")

# loading in data of oldG with newR
new_test_0.05 <- read_csv("OldG_newR_TestResults_circle_rad_0.05.csv")
new_test_0.1 <- read_csv("OldG_newR_TestResults_circle_rad_0.1.csv")
new_test_0.15 <- read_csv("OldG_newR_TestResults_circle_rad_0.15.csv")

# loading in data of newG with oldR 
new2_test_0.09 <- read_csv("NewG_OldR_TestResults_circle_rad_0.09.csv")
new2_test_0.1 <- read_csv("NewG_OldR_TestResults_circle_rad_0.1.csv")
new2_test_0.11 <- read_csv("NewG_OldR_TestResults_circle_rad_0.11.csv")
```

```{r wrangling orginal test parameters, echo=FALSE}
# give each circle a column of which test circle it came from. 
dat_0.09 <- test_0.09 %>% 
  mutate( test_circle = "Rad_0.09")
dat_0.1 <- test_0.1 %>% 
  mutate( test_circle = "Rad_0.1")
dat_0.11 <- test_0.11 %>% 
  mutate( test_circle = "Rad_0.11")


# binding rows of the data
all_dat <- bind_rows(dat_0.09, dat_0.1, dat_0.11) %>% 
  mutate(id = row_number()) %>% # give it an index
  rename("Search Radius" = "Radius")  
  #mutate(`Search Radius` = fct_inorder(as.factor(`Search Radius`))) ## results in error for chunk starting on line 201

### getting better labels on the facet_grid
label_all_dat <- all_dat

label_all_dat$Radius <- factor(label_all_dat$`Search Radius`, levels =c("0.09", "0.10", "0.11"),
                                    labels = c("0.09", "0.10", "0.11"))

### have to create a new data set then pivot longer the average count 
new <- all_dat %>% 
  select(-c(`Distance 1`, `Distance 2`, `Highest Vote`, "id")) %>% 
  pivot_longer(-c(`Search Radius`, Resolution, "test_circle"),
               names_to="Layer", 
               values_to = "Layer_Vote")
```


```{r wrangling of oldG with newR, echo=FALSE}
# give each circle a column of which test circle it came from. 
new_dat_0.05 <- new_test_0.05 %>% 
  mutate(test_circle = "Rad_0.05")
new_dat_0.1 <- new_test_0.1 %>% 
  mutate(test_circle = "Rad_0.1")
new_dat_0.15 <- new_test_0.15 %>% 
  mutate(test_circle = "Rad_0.15")


# binding rows of the data
new_all_dat <- bind_rows(new_dat_0.05, new_dat_0.1, new_dat_0.15) %>% 
  mutate(id = row_number()) %>% # give it an index
  rename("Search Radius" = "Radius")  
  #mutate(`Search Radius` = fct_inorder(as.factor(`Search Radius`))) ## results in error for chunk starting on line 201

### getting better labels on the facet_grid
new_label_all_dat <- new_all_dat

new_label_all_dat$Radius <- factor(new_label_all_dat$`Search Radius`, levels =c("0.05", "0.10", "0.15"),
                                    labels = c("0.05", "0.10", "0.15"))

### have to create a new data set then pivot longer the average count 
new1 <- new_all_dat %>% 
  select(-c(Gitter, `Distance 1`, `Distance 2`, id, Confidence)) %>% 
  rename("layer_0" = `Highest Vote`) %>%
  rename("Layer_01_mean" = `Layer 1 mean`) %>% 
  rename("Layer_02_mean" = `Layer 2 mean`) %>% 
  rename("Layer_03_mean" = `Layer 3 mean`) %>% 
  rename("Layer_04_mean" = `Layer 4 mean`) %>% 
  rename("Layer_05_mean" = `Layer 5 mean`) %>% 
  rename("Layer_06_mean" = `Layer 6 mean`) %>% 
  rename("Layer_07_mean" = `Layer 7 mean`) %>% 
  rename("Layer_08_mean" = `Layer 8 mean`) %>% 
  rename("Layer_09_mean" = `Layer 9 mean`) %>% 
  rename("Layer_10_mean" = `Layer 10 mean`) %>% 
  rename("Layer_11_mean" = `Layer 11 mean`) %>% 
  rename("Layer_12_mean" = `Layer 12 mean`) %>% 
  rename("Layer_13_mean" = `Layer 13 mean`) %>% 
  rename("Layer_14_mean" = `Layer 14 mean`) %>% 
  rename("Layer_15_mean" = `Layer 15 mean`) %>% 
  rename("Layer_16_mean" = `Layer 16 mean`) %>% 
  rename("Layer_17_mean" = `Layer 17 mean`) %>% 
  rename("Layer_18_mean" = `Layer 18 mean`) %>% 
  rename("Layer_19_mean" = `Layer 19 mean`) %>% 
  rename("Layer_20_mean" = `Layer 20 mean`) %>% 
  pivot_longer(-c(`Search Radius`, Resolution, "test_circle"),
               names_to="Layer", 
               values_to = "Layer_Vote")
```


```{r wrangling of newG with oldR, echo=FALSE}
# give each circle a column of which test circle it came from. 
new2_dat_0.09 <- new2_test_0.09 %>% 
  mutate(test_circle = "Rad_0.09")
new2_dat_0.1 <- new2_test_0.1 %>% 
  mutate(test_circle = "Rad_0.1")
new2_dat_0.11 <- new2_test_0.11 %>% 
  mutate(test_circle = "Rad_0.11")


# binding rows of the data
new2_all_dat <- bind_rows(new2_dat_0.09, new2_dat_0.1, new2_dat_0.11) %>% 
  mutate(id = row_number()) %>% # give it an index
  rename("Search Radius" = "Radius")  
  #mutate(`Search Radius` = fct_inorder(as.factor(`Search Radius`))) ## results in error for chunk starting on line 201

### getting better labels on the facet_grid
new2_label_all_dat <- new2_all_dat

new2_label_all_dat$Radius <- factor(new2_label_all_dat$`Search Radius`, levels =c("0.09", "0.10", "0.11"),
                                    labels = c("0.09", "0.10", "0.11"))

### have to create a new data set then pivot longer the average count 
new2 <- new2_all_dat %>% 
  select(-c(Gitter, `Distance 1`, `Distance 2`, id, Confidence)) %>% 
  rename("layer_0" = `Highest Vote`) %>%
  rename("Layer_01_mean" = `Layer 1 mean`) %>% 
  rename("Layer_02_mean" = `Layer 2 mean`) %>% 
  rename("Layer_03_mean" = `Layer 3 mean`) %>% 
  rename("Layer_04_mean" = `Layer 4 mean`) %>% 
  rename("Layer_05_mean" = `Layer 5 mean`) %>% 
  rename("Layer_06_mean" = `Layer 6 mean`) %>% 
  rename("Layer_07_mean" = `Layer 7 mean`) %>% 
  rename("Layer_08_mean" = `Layer 8 mean`) %>% 
  rename("Layer_09_mean" = `Layer 9 mean`) %>% 
  rename("Layer_10_mean" = `Layer 10 mean`) %>% 
  rename("Layer_11_mean" = `Layer 11 mean`) %>% 
  rename("Layer_12_mean" = `Layer 12 mean`) %>% 
  rename("Layer_13_mean" = `Layer 13 mean`) %>% 
  rename("Layer_14_mean" = `Layer 14 mean`) %>% 
  rename("Layer_15_mean" = `Layer 15 mean`) %>% 
  rename("Layer_16_mean" = `Layer 16 mean`) %>% 
  rename("Layer_17_mean" = `Layer 17 mean`) %>% 
  rename("Layer_18_mean" = `Layer 18 mean`) %>% 
  rename("Layer_19_mean" = `Layer 19 mean`) %>% 
  rename("Layer_20_mean" = `Layer 20 mean`) %>% 
  pivot_longer(-c(`Search Radius`, Resolution, "test_circle"),
               names_to="Layer", 
               values_to = "Layer_Vote")
```


# Graphs {.tabset .tabset-fade .tabset-pills}

- NOTE THE CHANGE IN SCALE BETWEEN THE GRAPHS - SCALES MAY BE INDEPENDENT.

## Line Graphs {.tabset .tabset-pills}

### Orginal parameters - Gitter 0.01 Radii: 0.09, 0.1, 0.11

#### Data from test circle of radius 0.09

```{r testRadius-0.09, echo=FALSE}

label_all_dat %>% 
  filter(test_circle == "Rad_0.09") %>%
  mutate(`Search Radius` = fct_inorder(as.factor(`Search Radius`))) %>% 
  ggplot(aes(group=Resolution)) +
  geom_point(aes(id, y=`Distance 1`), color="blue4") + 
  geom_line(aes(id, y=`Distance 1`), color="blue4") + 
  geom_point(aes(id, y=`Distance 2`)) + 
  geom_line(aes(id, y=`Distance 2`)) +
  facet_grid(`Search Radius`~Resolution,
             labeller=label_both, 
             scales = "free") + 
  labs(title = "Method 1 & 2 results from imperfect circle of radius 0.09", 
       subtitle = "Blue = Method 1",
       y = "Distance from dumd mean") +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), 
        axis.ticks.x = element_blank(),
        axis.title.y = element_text(size = 16))
```


#### Data from test circle of radius 0.1

```{r testRadius-0.1, echo=FALSE}
label_all_dat %>% 
  filter(test_circle == "Rad_0.1") %>%
  mutate(`Search Radius` = fct_inorder(as.factor(`Search Radius`))) %>% 
  ggplot(aes(group=Resolution)) +
  geom_point(aes(id, y=`Distance 1`), color="blue4") + 
  geom_line(aes(id, y=`Distance 1`), color="blue4") + 
  geom_point(aes(id, y=`Distance 2`)) + 
  geom_line(aes(id, y=`Distance 2`)) +
  facet_grid(`Search Radius`~Resolution,
             labeller=label_both, 
             scales = "free") + 
  labs(title = "Method 1 & 2 results from imperfect circle of radius 0.1", 
       subtitle = "Blue = Method 1",
       y = "Distance from dumd mean") +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), 
        axis.ticks.x = element_blank(),
        axis.title.y = element_text(size = 16))

```


#### Data from test circle of radius 0.11

```{r testRadius-0.11, echo=FALSE}
label_all_dat %>% 
  filter(test_circle == "Rad_0.11") %>%
  mutate(`Search Radius` = fct_inorder(as.factor(`Search Radius`))) %>% 
  ggplot(aes(group=Resolution)) +
  geom_point(aes(id, y=`Distance 1`), color="blue4") + 
  geom_line(aes(id, y=`Distance 1`), color="blue4") + 
  geom_point(aes(id, y=`Distance 2`)) + 
  geom_line(aes(id, y=`Distance 2`)) +
  facet_grid(`Search Radius`~Resolution,
             labeller=label_both, 
             scales = "free") + 
  labs(title = "Method 1 & 2 results from imperfect circle of radius 0.11", 
       subtitle = "Blue = Method 1",
       y = "Distance from dumd mean") +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), 
        axis.ticks.x = element_blank(),
        axis.title.y = element_text(size = 16))
```



### Gitter 0.03 with Radii: 0.09, 0.1, 0.11

#### Data from test circle of radius 0.09

```{r g:0.03 testRadius-0.09, echo=FALSE}
new2_label_all_dat %>% 
  filter(test_circle == "Rad_0.09") %>%
  mutate(`Search Radius` = fct_inorder(as.factor(`Search Radius`))) %>% 
  ggplot(aes(group=Resolution)) +
  geom_point(aes(id, y=`Distance 1`), color="blue4") + 
  geom_line(aes(id, y=`Distance 1`), color="blue4") + 
  geom_point(aes(id, y=`Distance 2`)) + 
  geom_line(aes(id, y=`Distance 2`)) +
  facet_grid(`Search Radius`~Resolution,
             labeller=label_both, 
             scales = "free") + 
  labs(title = "Method 1 & 2 results from imperfect circle of radius 0.09", 
       subtitle = "Blue = Method 1",
       y = "Distance from dumd mean") +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), 
        axis.ticks.x = element_blank(),
        axis.title.y = element_text(size = 16))
```


#### Data from test circle of radius 0.1

```{r g:0.03 testRadius-0.1, echo=FALSE}
new2_label_all_dat %>% 
  filter(test_circle == "Rad_0.1") %>%
  mutate(`Search Radius` = fct_inorder(as.factor(`Search Radius`))) %>% 
  ggplot(aes(group=Resolution)) +
  geom_point(aes(id, y=`Distance 1`), color="blue4") + 
  geom_line(aes(id, y=`Distance 1`), color="blue4") + 
  geom_point(aes(id, y=`Distance 2`)) + 
  geom_line(aes(id, y=`Distance 2`)) +
  facet_grid(`Search Radius`~Resolution,
             labeller=label_both, 
             scales = "free") + 
  labs(title = "Method 1 & 2 results from imperfect circle of radius 0.1", 
       subtitle = "Blue = Method 1",
       y = "Distance from dumd mean") +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), 
        axis.ticks.x = element_blank(),
        axis.title.y = element_text(size = 16))
```


#### Data from test circle of radius 0.11

```{r g:0.03 testRadius-0.11, echo=FALSE}
new2_label_all_dat %>% 
  filter(test_circle == "Rad_0.11") %>%
  mutate(`Search Radius` = fct_inorder(as.factor(`Search Radius`))) %>% 
  ggplot(aes(group=Resolution)) +
  geom_point(aes(id, y=`Distance 1`), color="blue4") + 
  geom_line(aes(id, y=`Distance 1`), color="blue4") + 
  geom_point(aes(id, y=`Distance 2`)) + 
  geom_line(aes(id, y=`Distance 2`)) +
  facet_grid(`Search Radius`~Resolution,
             labeller=label_both, 
             scales = "free") + 
  labs(title = "Method 1 & 2 results from imperfect circle of radius 0.11", 
       subtitle = "Blue = Method 1",
       y = "Distance from dumd mean") +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), 
        axis.ticks.x = element_blank(),
        axis.title.y = element_text(size = 16))
```


### Gitter 0.01 with Radii: 0.05, 0.1, 0.15 

#### Data from test circle of radius 0.05

```{r g:0.01 testRadius-0.05, echo=FALSE}
new_label_all_dat %>% 
  filter(test_circle == "Rad_0.05") %>%
  mutate(`Search Radius` = fct_inorder(as.factor(`Search Radius`))) %>% 
  ggplot(aes(group=Resolution)) +
  geom_point(aes(id, y=`Distance 1`), color="blue4") + 
  geom_line(aes(id, y=`Distance 1`), color="blue4") + 
  geom_point(aes(id, y=`Distance 2`)) + 
  geom_line(aes(id, y=`Distance 2`)) +
  facet_grid(`Search Radius`~Resolution,
             labeller=label_both, 
             scales = "free") + 
  labs(title = "Method 1 & 2 results from imperfect circle of radius 0.05", 
       subtitle = "Blue = Method 1",
       y = "Distance from dumd mean") +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), 
        axis.ticks.x = element_blank(),
        axis.title.y = element_text(size = 16))
```


#### Data from test circle of radius 0.1

```{r g:0.01 testRadius-0.1, echo=FALSE}
new_label_all_dat %>% 
  filter(test_circle == "Rad_0.1") %>%
  mutate(`Search Radius` = fct_inorder(as.factor(`Search Radius`))) %>% 
  ggplot(aes(group=Resolution)) +
  geom_point(aes(id, y=`Distance 1`), color="blue4") + 
  geom_line(aes(id, y=`Distance 1`), color="blue4") + 
  geom_point(aes(id, y=`Distance 2`)) + 
  geom_line(aes(id, y=`Distance 2`)) +
  facet_grid(`Search Radius`~Resolution,
             labeller=label_both, 
             scales = "free") + 
  labs(title = "Method 1 & 2 results from imperfect circle of radius 0.1", 
       subtitle = "Blue = Method 1",
       y = "Distance from dumd mean") +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), 
        axis.ticks.x = element_blank(),
        axis.title.y = element_text(size = 16))
```

#### Data from test circle of radius 0.15

```{r g:0.01 testRadius-0.15, echo=FALSE}
new_label_all_dat %>% 
  filter(test_circle == "Rad_0.15") %>%
  mutate(`Search Radius` = fct_inorder(as.factor(`Search Radius`))) %>% 
  ggplot(aes(group=Resolution)) +
  geom_point(aes(id, y=`Distance 1`), color="blue4") + 
  geom_line(aes(id, y=`Distance 1`), color="blue4") + 
  geom_point(aes(id, y=`Distance 2`)) + 
  geom_line(aes(id, y=`Distance 2`)) +
  facet_grid(`Search Radius`~Resolution,
             labeller=label_both, 
             scales = "free") + 
  labs(title = "Method 1 & 2 results from imperfect circle of radius 0.15", 
       subtitle = "Blue = Method 1",
       y = "Distance from dumd mean") +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), 
        axis.ticks.x = element_blank(),
        axis.title.y = element_text(size = 16))
```

## Distribution Graphs {.tabset .tabset-pills}

### Orginal parameters - Gitter 0.01 Radii: 0.09, 0.1, 0.11

#### Distribution of method 1

```{r Distance 1 distribution, echo=FALSE}
all_dat %>% 
  ggplot(aes(fct_inorder(as.factor(`Search Radius`)), y=`Distance 1`, color=fct_inorder(as.factor(`Search Radius`)))) +
  geom_boxplot() + 
  geom_jitter() +
  labs(title = "Overall Distribution of Method 1 by Radius and Resolution", 
       x = "Search Radius") +
  facet_grid(~Resolution, labeller = label_both) +
  theme(legend.position = "none", 
        axis.title.y = element_text(size = 16), 
        axis.title.x = element_text(size = 16))
```

#### Overal Distribution of method 1

```{r overall distribution, echo=FALSE}
### Overall distribution of method/Distance 1
all_dat %>% 
  ggplot(aes(fct_inorder(as.factor(`Search Radius`)), y=`Distance 1`, color=fct_inorder(as.factor(`Search Radius`)))) +
  geom_boxplot() + 
  geom_jitter() +
  labs(title = "Overall Distribution of Method 1 by Radius", 
       x = "Search Radius") +
  theme(legend.position = "none", 
        axis.title.y = element_text(size = 16), 
        axis.title.x = element_text(size = 16))
```

#### Distribution of Method 2

```{r Distance 2 Distribution}, echo=FALSE}
### distribution of method 2
all_dat %>% 
  ggplot(aes(fct_inorder(as.factor(`Search Radius`)), y=`Distance 2`, color=fct_inorder(as.factor(`Search Radius`)))) +
  geom_boxplot() + 
  geom_jitter() +
  labs(title = "Overall Distribution of Method 2 by Radius and Resolution", 
       x="Search Radius") +
  facet_grid(~Resolution, labeller = label_both) +
  theme(legend.position = "none", 
        axis.title.y = element_text(size = 16), 
        axis.title.x = element_text(size = 16))
```

#### Overall Distribution of Method 2

```{r overal distribution of method 2, echo=FALSE}
all_dat %>% 
  ggplot(aes(fct_inorder(as.factor(`Search Radius`)), y=`Distance 2`, color=fct_inorder(as.factor(`Search Radius`)))) +
  geom_boxplot() + 
  geom_jitter() +
  labs(title = "Overall Distribution of Method 2 by Radius", 
       x = "Search Radius") +
  theme(legend.position = "none", 
        axis.title.y = element_text(size = 16), 
        axis.title.x = element_text(size = 16))
```


### Gitter 0.03 with Radii: 0.09, 0.1, 0.11

#### Distribution of method 1 

```{r Distance 1 distribution g:0.03, echo=FALSE}
new2_all_dat %>% 
  ggplot(aes(fct_inorder(as.factor(`Search Radius`)), y=`Distance 1`, color=fct_inorder(as.factor(`Search Radius`)))) +
  geom_boxplot() + 
  geom_jitter() +
  labs(title = "Overall Distribution of Method 1 by Radius and Resolution", 
       x = "Search Radius") +
  facet_grid(~Resolution, labeller = label_both) +
  theme(legend.position = "none", 
        axis.title.y = element_text(size = 16), 
        axis.title.x = element_text(size = 16))
```


#### Overall Distribution of method 1

```{r Overall distribution Distance 1 g:0.03, echo=FALSE}
new2_all_dat %>% 
  ggplot(aes(fct_inorder(as.factor(`Search Radius`)), y=`Distance 1`, color=fct_inorder(as.factor(`Search Radius`)))) +
  geom_boxplot() + 
  geom_jitter() +
  labs(title = "Overall Distribution of Method 1 by Radius and Resolution", 
       x = "Search Radius") +
  theme(legend.position = "none", 
        axis.title.y = element_text(size = 16), 
        axis.title.x = element_text(size = 16))
```


#### Distribution of method 2 

```{r Distance 2 distribution g:0.03, echo=FALSE}
new2_all_dat %>% 
  ggplot(aes(fct_inorder(as.factor(`Search Radius`)), y=`Distance 2`, color=fct_inorder(as.factor(`Search Radius`)))) +
  geom_boxplot() + 
  geom_jitter() +
  labs(title = "Overall Distribution of Method 2 by Radius and Resolution", 
       x = "Search Radius") +
  facet_grid(~Resolution, labeller = label_both) +
  theme(legend.position = "none", 
        axis.title.y = element_text(size = 16), 
        axis.title.x = element_text(size = 16))
```


#### Overall Distribution of method 2

```{r Overall distribution Distance 2 g:0.03, echo=FALSE}
new2_all_dat %>% 
  ggplot(aes(fct_inorder(as.factor(`Search Radius`)), y=`Distance 2`, color=fct_inorder(as.factor(`Search Radius`)))) +
  geom_boxplot() + 
  geom_jitter() +
  labs(title = "Overall Distribution of Method 2 by Radius and Resolution", 
       x = "Search Radius") +
  theme(legend.position = "none", 
        axis.title.y = element_text(size = 16), 
        axis.title.x = element_text(size = 16))
```


### Gitter 0.01 with Radii: 0.05, 0.1, 0.15

#### Distribution of method 1

```{r Distance 1 distribution g:0.01, echo=FALSE}
new_all_dat %>% 
  ggplot(aes(fct_inorder(as.factor(`Search Radius`)), y=`Distance 1`, color=fct_inorder(as.factor(`Search Radius`)))) +
  geom_boxplot() + 
  geom_jitter() +
  labs(title = "Overall Distribution of Method 1 by Radius and Resolution", 
       x = "Search Radius") +
  facet_grid(~Resolution, labeller = label_both) +
  theme(legend.position = "none", 
        axis.title.y = element_text(size = 16), 
        axis.title.x = element_text(size = 16))
```


#### Overall Distribution of method 1

```{r Overall distribution Distance 1 g:0.01, echo=FALSE}
new_all_dat %>% 
  ggplot(aes(fct_inorder(as.factor(`Search Radius`)), y=`Distance 1`, color=fct_inorder(as.factor(`Search Radius`)))) +
  geom_boxplot() + 
  geom_jitter() +
  labs(title = "Overall Distribution of Method 1 by Radius", 
       x = "Search Radius") +
  theme(legend.position = "none", 
        axis.title.y = element_text(size = 16), 
        axis.title.x = element_text(size = 16))
```

#### Distribution of method 2

```{r Distance 2 distribution g:0.01, echo=FALSE}
new_all_dat %>% 
  ggplot(aes(fct_inorder(as.factor(`Search Radius`)), y=`Distance 2`, color=fct_inorder(as.factor(`Search Radius`)))) +
  geom_boxplot() + 
  geom_jitter() +
  labs(title = "Overall Distribution of Method 2 by Radius and Resolution", 
       x="Search Radius") +
  facet_grid(~Resolution, labeller = label_both) +
  theme(legend.position = "none", 
        axis.title.y = element_text(size = 16), 
        axis.title.x = element_text(size = 16))
```


#### Overall Distribution of method 2

```{r Overall Distribution distance 2 g:0.01, echo=FALSE}
new_all_dat %>% 
  ggplot(aes(fct_inorder(as.factor(`Search Radius`)), y=`Distance 2`, color=fct_inorder(as.factor(`Search Radius`)))) +
  geom_boxplot() + 
  geom_jitter() +
  labs(title = "Overall Distribution of Method 2 by Radius", 
       x="Search Radius") +
  theme(legend.position = "none", 
        axis.title.y = element_text(size = 16), 
        axis.title.x = element_text(size = 16))
```


## Bar Graphs {.tabset .tabset-pills}

### Orginal parameters - Gitter 0.01 Radii: 0.09, 0.1, 0.11

#### Overall Average Highest Votes

```{r overall, echo=FALSE, message=FALSE, warning=FALSE}
## bar plot with position dodge showing the mean of highest vote 
# extracting the vote and rounding. 
test <- all_dat %>%
  group_by(`Search Radius`, Resolution) %>% 
  summarise(avg_high_vote = mean(`Highest Vote`)) %>% 
  round(., digits = 2) %>% 
  pull(avg_high_vote)
 
all_dat %>% 
  group_by(`Search Radius`, Resolution) %>% 
  summarise(avg_high_vote = mean(`Highest Vote`)) %>% 
  ggplot(aes(x=fct_inorder(as.factor(`Search Radius`)), y=avg_high_vote, fill=`Search Radius`)) +
  geom_col(position = "dodge") +
  geom_text(aes(label=test), nudge_y = 1) +
  facet_grid(~Resolution, labeller = label_both) +
  labs(title = "Average Highest Vote by Radius and Resolution", 
       x = "Search Radius", 
       y = "Votes") +
  theme(legend.position = "position", 
        axis.title.y = element_text(size = 16), 
        axis.title.x = element_text(size = 16))
  #want to change color and order of Radius
```

#### Average highest vote for test circle of 0.09

```{r avg high vote 0.09, echo=FALSE, message=FALSE, warning=FALSE}
## bar plot with position dodge showing the mean of highest vote 
# extracting the vote and rounding.

#getting the proper numbers to label with  for test circle 0.01
test_9 <- all_dat %>%
  filter(test_circle == "Rad_0.09") %>% 
  group_by(`Search Radius`, Resolution) %>% 
  summarise(avg_high_vote = mean(`Highest Vote`)) %>% 
  round(., digits = 2) %>% 
  pull(avg_high_vote)
 
all_dat %>% 
  filter(test_circle == "Rad_0.09") %>% 
  group_by(`Search Radius`, Resolution) %>% 
  summarise(avg_high_vote = mean(`Highest Vote`)) %>% 
  ggplot(aes(x=fct_inorder(as.factor(`Search Radius`)), y=avg_high_vote, fill=`Search Radius`)) +
  geom_col(position = "dodge") +
  geom_text(aes(label=test_9), nudge_y = 1) +
  facet_grid(~Resolution, labeller = label_both) +
  labs(title = "Average Highest Vote by Radius and Resolution", 
       x = "Search Radius", 
       y = "Votes") +
  theme(legend.position = "position", 
        axis.title.y = element_text(size = 16), 
        axis.title.x = element_text(size = 16))
  #want to change color and order of Radius
```


#### Average highest vote for test circle of 0.1

```{r avg high vote 0.1, echo=FALSE, message=FALSE, warning=FALSE}
## bar plot with position dodge showing the mean of highest vote 
# extracting the vote and rounding.

test_1 <- all_dat %>%
  filter(test_circle == "Rad_0.1") %>% 
  group_by(`Search Radius`, Resolution) %>% 
  summarise(avg_high_vote = mean(`Highest Vote`)) %>% 
  round(., digits = 2) %>% 
  pull(avg_high_vote)

all_dat %>% 
  filter(test_circle == "Rad_0.1") %>% 
  group_by(`Search Radius`, Resolution) %>% 
  summarise(avg_high_vote = mean(`Highest Vote`)) %>% 
  ggplot(aes(x=fct_inorder(as.factor(`Search Radius`)), y=avg_high_vote, fill=`Search Radius`)) +
  geom_col(position = "dodge") +
  geom_text(aes(label=test_1), nudge_y = 1) +
  facet_grid(~Resolution, labeller = label_both) +
  labs(title = "Average Highest Vote by Radius and Resolution", 
       x = "Search Radius", 
       y = "Votes") +
  theme(legend.position = "position", 
        axis.title.y = element_text(size = 16), 
        axis.title.x = element_text(size = 16))
```


#### Average highest vote for test circle of 0.11

```{r avg high vote 0.11, echo=FALSE, message=FALSE, warning=FALSE}
## bar plot with position dodge showing the mean of highest vote 
# extracting the vote and rounding.
#getting the proper numbers to label with for test circle 0.011
test_11 <- all_dat %>%
  filter(test_circle == "Rad_0.11") %>% 
  group_by(`Search Radius`, Resolution) %>% 
  summarise(avg_high_vote = mean(`Highest Vote`)) %>% 
  round(., digits = 2) %>% 
  pull(avg_high_vote)

all_dat %>% 
  filter(test_circle == "Rad_0.11") %>%
  group_by(`Search Radius`, Resolution) %>% 
  summarise(avg_high_vote = mean(`Highest Vote`)) %>% 
  ggplot(aes(x=fct_inorder(as.factor(`Search Radius`)), y=avg_high_vote, fill=`Search Radius`)) +
  geom_col(position = "dodge") +
  geom_text(aes(label=test_11), nudge_y = 1) +
  facet_grid(~Resolution, labeller = label_both) +
  labs(title = "Average Highest Vote by Radius and Resolution", 
       x = "Search Radius", 
       y = "Votes") +
  theme(legend.position = "position", 
        axis.title.y = element_text(size = 16), 
        axis.title.x = element_text(size = 16))

```


### Gitter 0.03 with Radii: 0.09, 0.1, 0.11

#### Overall Highest Votes
```{r overall2, echo=FALSE, message=FALSE, warning=FALSE}
## bar plot with position dodge showing the mean of highest vote 
# extracting the vote and rounding. 
new2_test <- new2_all_dat %>%
  group_by(`Search Radius`, Resolution) %>% 
  summarise(avg_high_vote = mean(`Highest Vote`)) %>% 
  round(., digits = 2) %>% 
  pull(avg_high_vote)
 
new2_all_dat %>% 
  group_by(`Search Radius`, Resolution) %>% 
  summarise(avg_high_vote = mean(`Highest Vote`)) %>% 
  ggplot(aes(x=fct_inorder(as.factor(`Search Radius`)), y=avg_high_vote, fill=`Search Radius`)) +
  geom_col(position = "dodge") +
  geom_text(aes(label=new2_test), nudge_y = 1) +
  facet_grid(~Resolution, labeller = label_both) +
  labs(title = "Average Highest Vote by Radius and Resolution", 
       x = "Search Radius", 
       y = "Votes") +
  theme(legend.position = "position", 
        axis.title.y = element_text(size = 16), 
        axis.title.x = element_text(size = 16))
```


#### Average highest vote for test circle of radius 0.09

```{r avg high vote2 g0.03 r0.09, echo=FALSE, message=FALSE, warning=FALSE}
## bar plot with position dodge showing the mean of highest vote 
# extracting the vote and rounding.

#getting the proper numbers to label with  for test circle 0.01
new2_test_9 <- new2_all_dat %>%
  filter(test_circle == "Rad_0.09") %>% 
  group_by(`Search Radius`, Resolution) %>% 
  summarise(avg_high_vote = mean(`Highest Vote`)) %>% 
  round(., digits = 2) %>% 
  pull(avg_high_vote)
 
new2_all_dat %>% 
  filter(test_circle == "Rad_0.09") %>% 
  group_by(`Search Radius`, Resolution) %>% 
  summarise(avg_high_vote = mean(`Highest Vote`)) %>% 
  ggplot(aes(x=fct_inorder(as.factor(`Search Radius`)), y=avg_high_vote, fill=`Search Radius`)) +
  geom_col(position = "dodge") +
  geom_text(aes(label=new2_test_9), nudge_y = 1) +
  facet_grid(~Resolution, labeller = label_both) +
  labs(title = "Average Highest Vote by Radius and Resolution", 
       x = "Search Radius", 
       y = "Votes") +
  theme(legend.position = "position", 
        axis.title.y = element_text(size = 16), 
        axis.title.x = element_text(size = 16))
```


#### Average highest vote for test circle of radius 0.1

```{r avg high vote2 g0.03 r0.1, echo=FALSE, message=FALSE, warning=FALSE}
## bar plot with position dodge showing the mean of highest vote 
# extracting the vote and rounding.

#getting the proper numbers to label with  for test circle 0.01
new2_test_1 <- new2_all_dat %>%
  filter(test_circle == "Rad_0.1") %>% 
  group_by(`Search Radius`, Resolution) %>% 
  summarise(avg_high_vote = mean(`Highest Vote`)) %>% 
  round(., digits = 2) %>% 
  pull(avg_high_vote)
 
new2_all_dat %>% 
  filter(test_circle == "Rad_0.1") %>% 
  group_by(`Search Radius`, Resolution) %>% 
  summarise(avg_high_vote = mean(`Highest Vote`)) %>% 
  ggplot(aes(x=fct_inorder(as.factor(`Search Radius`)), y=avg_high_vote, fill=`Search Radius`)) +
  geom_col(position = "dodge") +
  geom_text(aes(label=new2_test_1), nudge_y = 1) +
  facet_grid(~Resolution, labeller = label_both) +
  labs(title = "Average Highest Vote by Radius and Resolution", 
       x = "Search Radius", 
       y = "Votes") +
  theme(legend.position = "position", 
        axis.title.y = element_text(size = 16), 
        axis.title.x = element_text(size = 16))
```


#### Average highest vote for test circle of radius 0.11

```{r avg high vote2 g0.03 r0.11, echo=FALSE, message=FALSE, warning=FALSE}
## bar plot with position dodge showing the mean of highest vote 
# extracting the vote and rounding.

#getting the proper numbers to label with  for test circle 0.01
new2_test_11 <- new2_all_dat %>%
  filter(test_circle == "Rad_0.11") %>% 
  group_by(`Search Radius`, Resolution) %>% 
  summarise(avg_high_vote = mean(`Highest Vote`)) %>% 
  round(., digits = 2) %>% 
  pull(avg_high_vote)
 
new2_all_dat %>% 
  filter(test_circle == "Rad_0.11") %>% 
  group_by(`Search Radius`, Resolution) %>% 
  summarise(avg_high_vote = mean(`Highest Vote`)) %>% 
  ggplot(aes(x=fct_inorder(as.factor(`Search Radius`)), y=avg_high_vote, fill=`Search Radius`)) +
  geom_col(position = "dodge") +
  geom_text(aes(label=new2_test_11), nudge_y = 1) +
  facet_grid(~Resolution, labeller = label_both) +
  labs(title = "Average Highest Vote by Radius and Resolution", 
       x = "Search Radius", 
       y = "Votes") +
  theme(legend.position = "position", 
        axis.title.y = element_text(size = 16), 
        axis.title.x = element_text(size = 16))
```


### Gitter 0.01 with Radii: 0.05, 0.1, 0.15 

#### Overall Highest Votes

```{r overall3, echo=FALSE, message=FALSE, warning=FALSE}
## bar plot with position dodge showing the mean of highest vote 
# extracting the vote and rounding. 
new_test <- new_all_dat %>%
  group_by(`Search Radius`, Resolution) %>% 
  summarise(avg_high_vote = mean(`Highest Vote`)) %>% 
  round(., digits = 2) %>% 
  pull(avg_high_vote)
 
new_all_dat %>% 
  group_by(`Search Radius`, Resolution) %>% 
  summarise(avg_high_vote = mean(`Highest Vote`)) %>% 
  ggplot(aes(x=fct_inorder(as.factor(`Search Radius`)), y=avg_high_vote, fill=`Search Radius`)) +
  geom_col(position = "dodge") +
  geom_text(aes(label=new_test), nudge_y = 1) +
  facet_grid(~Resolution, labeller = label_both) +
  labs(title = "Average Highest Vote by Radius and Resolution", 
       x = "Search Radius", 
       y = "Votes") +
  theme(legend.position = "position", 
        axis.title.y = element_text(size = 16), 
        axis.title.x = element_text(size = 16))
```


#### Average highest vote for test circle of radius 0.05

```{r avg high vote3 g0.01 r0.05, echo=FALSE, message=FALSE, warning=FALSE}
## bar plot with position dodge showing the mean of highest vote 
# extracting the vote and rounding.

#getting the proper numbers to label with  for test circle 0.01
test_5 <- new_all_dat %>%
  filter(test_circle == "Rad_0.05") %>% 
  group_by(`Search Radius`, Resolution) %>% 
  summarise(avg_high_vote = mean(`Highest Vote`)) %>% 
  round(., digits = 2) %>% 
  pull(avg_high_vote)
 
new_all_dat %>% 
  filter(test_circle == "Rad_0.05") %>% 
  group_by(`Search Radius`, Resolution) %>% 
  summarise(avg_high_vote = mean(`Highest Vote`)) %>% 
  ggplot(aes(x=fct_inorder(as.factor(`Search Radius`)), y=avg_high_vote, fill=`Search Radius`)) +
  geom_col(position = "dodge") +
  geom_text(aes(label=test_5), nudge_y = 1) +
  facet_grid(~Resolution, labeller = label_both) +
  labs(title = "Average Highest Vote by Radius and Resolution", 
       x = "Search Radius", 
       y = "Votes") +
  theme(legend.position = "position", 
        axis.title.y = element_text(size = 16), 
        axis.title.x = element_text(size = 16))
```


#### Average highest vote for test circle of radius 0.1

```{r avg high vote3 g0.01 r0.1, echo=FALSE, message=FALSE, warning=FALSE}
## bar plot with position dodge showing the mean of highest vote 
# extracting the vote and rounding.

#getting the proper numbers to label with  for test circle 0.01
test_1 <- new_all_dat %>%
  filter(test_circle == "Rad_0.1") %>% 
  group_by(`Search Radius`, Resolution) %>% 
  summarise(avg_high_vote = mean(`Highest Vote`)) %>% 
  round(., digits = 2) %>% 
  pull(avg_high_vote)
 
new_all_dat %>% 
  filter(test_circle == "Rad_0.1") %>% 
  group_by(`Search Radius`, Resolution) %>% 
  summarise(avg_high_vote = mean(`Highest Vote`)) %>% 
  ggplot(aes(x=fct_inorder(as.factor(`Search Radius`)), y=avg_high_vote, fill=`Search Radius`)) +
  geom_col(position = "dodge") +
  geom_text(aes(label=test_1), nudge_y = 1) +
  facet_grid(~Resolution, labeller = label_both) +
  labs(title = "Average Highest Vote by Radius and Resolution", 
       x = "Search Radius", 
       y = "Votes") +
  theme(legend.position = "position", 
        axis.title.y = element_text(size = 16), 
        axis.title.x = element_text(size = 16))
```


#### Average highest vote for test circle of radius 0.15

```{r avg high vote3 g0.01 r0.15, echo=FALSE, message=FALSE, warning=FALSE}
## bar plot with position dodge showing the mean of highest vote 
# extracting the vote and rounding.

#getting the proper numbers to label with  for test circle 0.01
test_15 <- new_all_dat %>%
  filter(test_circle == "Rad_0.15") %>% 
  group_by(`Search Radius`, Resolution) %>% 
  summarise(avg_high_vote = mean(`Highest Vote`)) %>% 
  round(., digits = 2) %>% 
  pull(avg_high_vote)
 
new_all_dat %>% 
  filter(test_circle == "Rad_0.15") %>% 
  group_by(`Search Radius`, Resolution) %>% 
  summarise(avg_high_vote = mean(`Highest Vote`)) %>% 
  ggplot(aes(x=fct_inorder(as.factor(`Search Radius`)), y=avg_high_vote, fill=`Search Radius`)) +
  geom_col(position = "dodge") +
  geom_text(aes(label=test_15), nudge_y = 1) +
  facet_grid(~Resolution, labeller = label_both) +
  labs(title = "Average Highest Vote by Radius and Resolution", 
       x = "Search Radius", 
       y = "Votes") +
  theme(legend.position = "position", 
        axis.title.y = element_text(size = 16), 
        axis.title.x = element_text(size = 16))
```

## Average Layer Mean {.tabset .tabset-pills}

### Orginal parameters - Gitter 0.01 Radii: 0.09, 0.1, 0.11

#### Average Layer Vote

```{r avg layer mean, echo=FALSE, message=FALSE, warning=FALSE}
# NEED TO ADD LAYER ZERO

new %>% 
  group_by(`Search Radius`, Resolution, test_circle, Layer) %>% 
  summarise(lay_avg = mean(Layer_Vote)) %>% 
  ggplot(aes(x=test_circle, y=lay_avg, group=Layer, fill=Layer))+
  geom_col(position ="dodge") + 
  facet_grid(`Search Radius`~Resolution, labeller = label_both, scales = "free") + 
  labs(title = "Average vote every box outside the highest vote",
       y="Average layer vote", 
       x="Test circle") +
  theme(axis.text.x = element_text(angle = 90), 
        axis.title.y = element_text(size = 16), 
        axis.title.x = element_text(size = 16))
```


### Gitter 0.03 with Radii: 0.09, 0.1, 0.11

#### Average Layer Vote
```{r avg layer mean2, echo=FALSE, message=FALSE, warning=FALSE}
new2 %>% 
  group_by(`Search Radius`, Resolution, test_circle, Layer) %>% 
  summarise(lay_avg = mean(Layer_Vote)) %>% 
  ggplot(aes(x=test_circle, y=lay_avg, group=Layer, fill=Layer))+
  geom_col(position ="dodge") + 
  facet_grid(`Search Radius`~Resolution, labeller = label_both, scales = "free") + 
  labs(title = "Average vote every box outside the highest vote",
       y="Average layer vote", 
       x="Test circle") +
  theme(axis.text.x = element_text(angle = 90), 
        axis.title.y = element_text(size = 16), 
        axis.title.x = element_text(size = 16))
```

#### Average Confidence

```{r table of confidence2, echo=FALSE}

```


### Gitter 0.01 with Radii: 0.05, 0.1, 0.15

#### Average Layer Vote
```{r avg layer mean3, echo=FALSE, message=FALSE, warning=FALSE}
new1 %>% 
  group_by(`Search Radius`, Resolution, test_circle, Layer) %>% 
  summarise(lay_avg = mean(Layer_Vote)) %>% 
  ggplot(aes(x=test_circle, y=lay_avg, group=Layer, fill=Layer))+
  geom_col(position ="dodge") + 
  facet_grid(`Search Radius`~Resolution, labeller = label_both, scales = "free") + 
  labs(title = "Average vote every box outside the highest vote",
       y="Average layer vote", 
       x="Test circle") +
  theme(axis.text.x = element_text(angle = 90), 
        axis.title.y = element_text(size = 16), 
        axis.title.x = element_text(size = 16))
```



## Confidence Graphs {.tabset .tabset-pills}

### Gitter 0.03 with Radii: 0.09, 0.1, 0.11

#### Data from test circle of radius 0.09

```{r avg confindence g0.03 rad_0.09, echo=FALSE, message=FALSE, warning=FALSE}
conf2 <- new2_label_all_dat %>% 
  select(-c(4:26)) %>% 
  select(-c(Gitter, Radius, id)) %>%
  group_by(Resolution, `Search Radius`, test_circle) %>%
  summarise(conf_avg = mean(Confidence))

num2_9 <- conf2 %>%
  filter(test_circle == "Rad_0.09") %>% 
  select(-c(`Search Radius`, Resolution, test_circle)) %>%
  round(., digits = 3) %>%
  pull(conf_avg)
  

new2_label_all_dat %>% 
  filter(test_circle == "Rad_0.09") %>% 
  group_by(Resolution, `Search Radius`) %>%
  summarise(conf_avg = mean(Confidence)) %>% 
  mutate(`Search Radius` = fct_inorder(as.factor(`Search Radius`))) %>% 
  ggplot(aes(x=`Search Radius`, y=conf_avg, fill=`Search Radius`)) +
  geom_col() +
  geom_text(aes(label=num2_9), nudge_y = 0.025) +
  facet_grid(~Resolution, labeller = label_both) + 
  labs(title = "Average confidence", 
       subtitle = "from 0 to 1", 
       x= "Search Radius", 
       y= "Average confidence") + 
  theme(legend.position = "none",
        axis.title.x = element_text(size = 16),
        axis.title.y = element_text(size = 16))
```


#### Data from test circle of radius 0.1

```{r avg confindence g0.03 rad_0.1, echo=FALSE, message=FALSE, warning=FALSE}
num2_1 <- conf2 %>%
  filter(test_circle == "Rad_0.1") %>% 
  select(-c(`Search Radius`, Resolution, test_circle)) %>%
  round(., digits = 3) %>%
  pull(conf_avg)

new2_label_all_dat %>% 
  filter(test_circle == "Rad_0.1") %>% 
  group_by(Resolution, `Search Radius`) %>%
  summarise(conf_avg = mean(Confidence)) %>%
  mutate(`Search Radius` = fct_inorder(as.factor(`Search Radius`))) %>% 
  ggplot(aes(x=`Search Radius`, y=conf_avg, fill=`Search Radius`)) +
  geom_col() +
  geom_text(aes(label=num2_1), nudge_y = 0.025) +
  facet_grid(~Resolution, labeller = label_both) +
  labs(title = "Average confidence", 
       subtitle = "from 0 to 1", 
       x= "Search Radius", 
       y= "Average confidence") + 
  theme(legend.position = "none",
        axis.title.x = element_text(size = 16),
        axis.title.y = element_text(size = 16))
```


#### Data from test circle of radius 0.11

```{r avg confindence g0.03 rad_0.11, echo=FALSE, message=FALSE, warning=FALSE}
num2_11 <- conf2 %>%
  filter(test_circle == "Rad_0.11") %>% 
  select(-c(`Search Radius`, Resolution, test_circle)) %>%
  round(., digits = 3) %>%
  pull(conf_avg)

new2_label_all_dat %>% 
  filter(test_circle == "Rad_0.11") %>% 
  group_by(Resolution, `Search Radius`) %>%
  summarise(conf_avg = mean(Confidence)) %>%
  mutate(`Search Radius` = fct_inorder(as.factor(`Search Radius`))) %>% 
  ggplot(aes(x=`Search Radius`, y=conf_avg, fill=`Search Radius`)) +
  geom_col() +
  geom_text(aes(label=num2_11), nudge_y = 0.025) +
  facet_grid(~Resolution, labeller = label_both) +
  labs(title = "Average confidence", 
       subtitle = "from 0 to 1", 
       x= "Search Radius", 
       y= "Average confidence") + 
  theme(legend.position = "none",
        axis.title.x = element_text(size = 16),
        axis.title.y = element_text(size = 16))
```


### Gitter 0.01 with Radii: 0.05, 0.1, 0.15

#### Table of all results

```{r confidence table, echo=FALSE, message=FALSE, warning=FALSE}
# creating dataset needed
conf <- new_label_all_dat %>% 
  select(-c(4:26)) %>% 
  select(-c(Gitter, Radius, id)) %>%
  group_by(Resolution, `Search Radius`, test_circle) %>%
  summarise(conf_avg = mean(Confidence))

# making it wider
conf_wider <- conf %>% 
  pivot_wider(names_from = Resolution, values_from=conf_avg)

datatable(conf_wider)
```

#### Data from test circle of radius 0.05

```{r avg confindence g0.01 rad_0.05, echo=FALSE, message=FALSE, warning=FALSE}
conf <- new_label_all_dat %>% 
  select(-c(4:26)) %>% 
  select(-c(Gitter, Radius, id)) %>%
  group_by(Resolution, `Search Radius`, test_circle) %>%
  summarise(conf_avg = mean(Confidence))

num_5 <- conf %>%
  filter(test_circle == "Rad_0.05") %>% 
  select(-c(`Search Radius`, Resolution, test_circle)) %>%
  round(., digits = 3) %>%
  pull(conf_avg)
  

new_label_all_dat %>% 
  filter(test_circle == "Rad_0.05") %>% 
  group_by(Resolution, `Search Radius`) %>%
  summarise(conf_avg = mean(Confidence)) %>% 
  mutate(`Search Radius` = fct_inorder(as.factor(`Search Radius`))) %>% 
  ggplot(aes(x=`Search Radius`, y=conf_avg, fill=`Search Radius`)) +
  geom_col() +
  geom_text(aes(label=num_5), nudge_y = 0.025) +
  facet_grid(~Resolution, labeller = label_both) + 
  labs(title = "Average confidence", 
       subtitle = "from 0 to 1", 
       x= "Search Radius", 
       y= "Average confidence") + 
  theme(legend.position = "none",
        axis.title.x = element_text(size = 16),
        axis.title.y = element_text(size = 16))
```

#### Data from test circle of radius 0.1

```{r avg confindence g0.01 rad_0.1, echo=FALSE, message=FALSE, warning=FALSE}
num_1 <- conf %>%
  filter(test_circle == "Rad_0.1") %>% 
  select(-c(`Search Radius`, Resolution, test_circle)) %>%
  round(., digits = 3) %>%
  pull(conf_avg)

new_label_all_dat %>% 
  filter(test_circle == "Rad_0.1") %>% 
  group_by(Resolution, `Search Radius`) %>%
  summarise(conf_avg = mean(Confidence)) %>%
  mutate(`Search Radius` = fct_inorder(as.factor(`Search Radius`))) %>% 
  ggplot(aes(x=`Search Radius`, y=conf_avg, fill=`Search Radius`)) +
  geom_col() +
  geom_text(aes(label=num_1), nudge_y = 0.025) +
  facet_grid(~Resolution, labeller = label_both) +
  labs(title = "Average confidence", 
       subtitle = "from 0 to 1", 
       x= "Search Radius", 
       y= "Average confidence") + 
  theme(legend.position = "none",
        axis.title.x = element_text(size = 16),
        axis.title.y = element_text(size = 16))
```

#### Data from test circle of radius 0.15

```{r avg confindence g0.01 rad_0.15, echo=FALSE, message=FALSE, warning=FALSE}
num_15 <- conf %>%
  filter(test_circle == "Rad_0.15") %>% 
  select(-c(`Search Radius`, Resolution, test_circle)) %>%
  round(., digits = 3) %>%
  pull(conf_avg)

new_label_all_dat %>% 
  filter(test_circle == "Rad_0.15") %>% 
  group_by(Resolution, `Search Radius`) %>%
  summarise(conf_avg = mean(Confidence)) %>%
  mutate(`Search Radius` = fct_inorder(as.factor(`Search Radius`))) %>% 
  ggplot(aes(x=`Search Radius`, y=conf_avg, fill=`Search Radius`)) +
  geom_col() +
  geom_text(aes(label=num_15), nudge_y = 0.025) +
  facet_grid(~Resolution, labeller = label_both) +
  labs(title = "Average confidence", 
       subtitle = "from 0 to 1", 
       x= "Search Radius", 
       y= "Average confidence") + 
  theme(legend.position = "none",
        axis.title.x = element_text(size = 16),
        axis.title.y = element_text(size = 16))
```

