---
title: "RBDC Presentation"
author: "Matthew Goodsell"
date: "6/10/2020"
output:
  html_document:
   keep_md: TRUE 
---

```{r packages & loading data, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

# loading packages
pacman::p_load(tidyverse)

# loading in data
test_0.09 <- read_csv("modified_TestResults_circle_rad_0.09.csv")

test_0.1 <- read_csv("modified_TestResults_circle_rad_0.10.csv")

test_0.11 <- read_csv("modified_TestResults_circle_rad_0.11.csv")
```

```{r wrangling data}
# give each circle a column of which test circle it came from. 
dat_0.09 <- test_0.09 %>% 
  mutate( test_circle = "Rad_0.09")

dat_0.1 <- test_0.1 %>% 
  mutate( test_circle = "Rad_0.1")

dat_0.11 <- test_0.11 %>% 
  mutate( test_circle = "Rad_0.11")


# binding rows of the data
all_dat <- bind_rows(dat_0.09, dat_0.1, dat_0.11) %>% 
  mutate(id = row_number()) # give it an index

### getting better labels on the facet_grid
label_all_dat <- all_dat

label_all_dat$Radius <- factor(label_all_dat$Radius, levels =c("0.099", "0.01", "0.011"),
                               labels = c("0.099", " 0.010", "0.011"))
```

# Graphs {.tabset .tabset-fade .tabset-pills}

To do:  

- create boxplot graph to show the spread of the distribution for method 2
- Create a bar graph for an aver layer mean. 

## Line Graphs 

### Data from test circle of radius 0.099

```{r testRadius-0.099}

label_all_dat %>% 
  filter(test_circle == "Rad_0.09") %>%
  ggplot(aes(group=Resolution)) +
  geom_point(aes(id, y=`Distance 1`), color="blue4") + 
  geom_line(aes(id, y=`Distance 1`), color="blue4") + 
  geom_point(aes(id, y=`Distance 2`)) + 
  geom_line(aes(id, y=`Distance 2`)) +
  facet_grid(Radius~Resolution,
             labeller=label_both) + 
  labs(title = "Method 1 & 2 results from imperfect circle of radius 0.09", 
       subtitle = "Blue = Method 1",
       y = "Distance from dumd mean") +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), 
        axis.ticks.x = element_blank(), 
        strip.background = element_rect(fill="grey48"))
```

### Data from test circle of radius 0.01

```{r testRadius-0.01}
label_all_dat %>% 
  filter(test_circle == "Rad_0.1") %>%
  ggplot(aes(group=Resolution)) +
  geom_point(aes(id, y=`Distance 1`), color="blue4") + 
  geom_line(aes(id, y=`Distance 1`), color="blue4") + 
  geom_point(aes(id, y=`Distance 2`)) + 
  geom_line(aes(id, y=`Distance 2`)) +
  facet_grid(Radius~Resolution,
             labeller=label_both, 
             scales = "free") + 
  labs(title = "Method 1 & 2 results from imperfect circle of radius 0.09", 
       subtitle = "Blue = Method 1",
       y = "Distance from dumd mean") +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), 
        axis.ticks.x = element_blank(), 
        strip.background = element_rect(fill="grey48"))

```


### Data from test circle of radius 0.011

```{r testRadius-0.011, echo=FALSE}
label_all_dat %>% 
  filter(test_circle == "Rad_0.11") %>%
  ggplot(aes(group=Resolution)) +
  geom_point(aes(id, y=`Distance 1`), color="blue4") + 
  geom_line(aes(id, y=`Distance 1`), color="blue4") + 
  geom_point(aes(id, y=`Distance 2`)) + 
  geom_line(aes(id, y=`Distance 2`)) +
  facet_grid(Radius~Resolution,
             labeller=label_both, 
             scales = "free") + 
  labs(title = "Method 1 & 2 results from imperfect circle of radius 0.09", 
       subtitle = "Blue = Method 1",
       y = "Distance from dumd mean") +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), 
        axis.ticks.x = element_blank(), 
        strip.background = element_rect(fill="grey48"))
```


## Distribution graphs

### Distribution of method 1

```{r Distance 1 distribution}
all_dat %>% 
  ggplot(aes(fct_inorder(as.factor(Radius)), y=`Distance 1`, color=fct_inorder(as.factor(Radius)))) +
  geom_boxplot() + 
  geom_jitter() +
  labs(title = "Overall Distribution of Method 1 by Radius and Resolution", 
       x = "Search Radius") +
  facet_grid(~Resolution, labeller = label_both) +
  theme(legend.position = "none")
```

### Overal Distribution of method 1

```{r overall distribution}
### Overall distribution of method/Distance 1
all_dat %>% 
  ggplot(aes(fct_inorder(as.factor(Radius)), y=`Distance 1`, color=fct_inorder(as.factor(Radius)))) +
  geom_boxplot() + 
  geom_jitter() +
  labs(title = "Overall Distribution of Method 1 by Radius", 
       x = "Search Radius") +
  theme(legend.position = "none")
```

### Distribution of Method 2

```{r Distance 2 Distribution}
### distribution of method 2
all_dat %>% 
  ggplot(aes(fct_inorder(as.factor(Radius)), y=`Distance 2`, color=fct_inorder(as.factor(Radius)))) +
  geom_boxplot() + 
  geom_jitter() +
  labs(title = "Overall Distribution of Method 2 by Radius and Resolution", 
       x="Search Radius") +
  facet_grid(~Resolution, labeller = label_both) +
  theme(legend.position = "none")
```

### Overall Distribution of Method 2

```{r}
all_dat %>% 
  ggplot(aes(fct_inorder(as.factor(Radius)), y=`Distance 2`, color=fct_inorder(as.factor(Radius)))) +
  geom_boxplot() + 
  geom_jitter() +
  labs(title = "Overall Distribution of Method 2 by Radius", 
       x = "Search Radius")
```

## Bar plots of Average Votes

### Overall Average Highest Votes

```{r overall}
## bar plot with position dodge showing the mean of highest vote 
# extracting the vote and rounding. 
test <- all_dat %>%
  group_by(Radius, Resolution) %>% 
  summarise(avg_high_vote = mean(`Highest Vote`)) %>% 
  round(., digits = 2) %>% 
  pull(avg_high_vote)
 
all_dat %>% 
  group_by(Radius, Resolution) %>% 
  summarise(avg_high_vote = mean(`Highest Vote`)) %>% 
  ggplot(aes(x=fct_inorder(as.factor(Radius)), y=avg_high_vote, fill=Radius)) +
  geom_col(position = "dodge") +
  geom_text(aes(label=test), nudge_y = 1) +
  facet_grid(~Resolution, labeller = label_both) +
  labs(title = "Average Highest Vote by Radius and Resolution", 
       x = "Search Radius", 
       y = "Votes") +
  theme(legend.position = "position", 
        axis.title.y = element_text(size = 16), 
        axis.title.x = element_text(size = 16))
  #want to change color and order of Radius
```

### Average highest vote for test circle of 0.09

```{r}
## bar plot with position dodge showing the mean of highest vote 
# extracting the vote and rounding.

#getting the proper numbers to label with  for test circle 0.01
test_9 <- all_dat %>%
  filter(test_circle == "Rad_0.09") %>% 
  group_by(Radius, Resolution) %>% 
  summarise(avg_high_vote = mean(`Highest Vote`)) %>% 
  round(., digits = 2) %>% 
  pull(avg_high_vote)
 
all_dat %>% 
  filter(test_circle == "Rad_0.09") %>% 
  group_by(Radius, Resolution) %>% 
  summarise(avg_high_vote = mean(`Highest Vote`)) %>% 
  ggplot(aes(x=fct_inorder(as.factor(Radius)), y=avg_high_vote, fill=Radius)) +
  geom_col(position = "dodge") +
  geom_text(aes(label=test_9), nudge_y = 1) +
  facet_grid(~Resolution, labeller = label_both) +
  labs(title = "Average Highest Vote by Radius and Resolution", 
       x = "Search Radius", 
       y = "Votes") +
  theme(legend.position = "position", 
        axis.title.y = element_text(size = 16), 
        axis.title.x = element_text(size = 16))
  #want to change color and order of Radius
```


### Average highest vote for test circle of 0.01

```{r}
## bar plot with position dodge showing the mean of highest vote 
# extracting the vote and rounding.

test_1 <- all_dat %>%
  filter(test_circle == "Rad_0.1") %>% 
  group_by(Radius, Resolution) %>% 
  summarise(avg_high_vote = mean(`Highest Vote`)) %>% 
  round(., digits = 2) %>% 
  pull(avg_high_vote)

all_dat %>% 
  filter(test_circle == "Rad_0.1") %>% 
  group_by(Radius, Resolution) %>% 
  summarise(avg_high_vote = mean(`Highest Vote`)) %>% 
  ggplot(aes(x=fct_inorder(as.factor(Radius)), y=avg_high_vote, fill=Radius)) +
  geom_col(position = "dodge") +
  geom_text(aes(label=test_1), nudge_y = 1) +
  facet_grid(~Resolution, labeller = label_both) +
  labs(title = "Average Highest Vote by Radius and Resolution", 
       x = "Search Radius", 
       y = "Votes") +
  theme(legend.position = "position", 
        axis.title.y = element_text(size = 16), 
        axis.title.x = element_text(size = 16))
```


### Average highest vote for test circle of 0.011

```{r}
## bar plot with position dodge showing the mean of highest vote 
# extracting the vote and rounding.
#getting the proper numbers to label with for test circle 0.011
test_11 <- all_dat %>%
  filter(test_circle == "Rad_0.11") %>% 
  group_by(Radius, Resolution) %>% 
  summarise(avg_high_vote = mean(`Highest Vote`)) %>% 
  round(., digits = 2) %>% 
  pull(avg_high_vote)

all_dat %>% 
  filter(test_circle == "Rad_0.11") %>%
  group_by(Radius, Resolution) %>% 
  summarise(avg_high_vote = mean(`Highest Vote`)) %>% 
  ggplot(aes(x=fct_inorder(as.factor(Radius)), y=avg_high_vote, fill=Radius)) +
  geom_col(position = "dodge") +
  geom_text(aes(label=test_11), nudge_y = 1) +
  facet_grid(~Resolution, labeller = label_both) +
  labs(title = "Average Highest Vote by Radius and Resolution", 
       x = "Search Radius", 
       y = "Votes") +
  theme(legend.position = "position", 
        axis.title.y = element_text(size = 16), 
        axis.title.x = element_text(size = 16))

```


## Average Layer mean 

```{r}

```


