---
title: "Test Results for: Gitter=0.01 & Radii=0.05, 0.1, 0.15"
author: "Matthew Goodsell"
date: "6/22/2020"
output: 
  html_document:
   keep_md: TRUE 
---

```{r packages & loading data, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

# loading package
pacman::p_load(tidyverse, DT)

# loading in data
new_test_0.05 <- read_csv("Data/OldG_newR_TestResults_circle_rad_0.05.csv")

new_test_0.1 <- read_csv("Data/OldG_newR_TestResults_circle_rad_0.1.csv")

new_test_0.15 <- read_csv("Data/OldG_newR_TestResults_circle_rad_0.15.csv")

```

```{r wrangling data, echo=FALSE}
# give each circle a column of which test circle it came from. 
new_dat_0.05 <- new_test_0.05 %>% 
  mutate(test_circle = "Rad_0.05")

new_dat_0.1 <- new_test_0.1 %>% 
  mutate(test_circle = "Rad_0.1")

new_dat_0.15 <- new_test_0.15 %>% 
  mutate(test_circle = "Rad_0.15")


# binding rows of the data
new_all_dat <- bind_rows(new_dat_0.05, new_dat_0.1, new_dat_0.15) %>% 
  mutate(id = row_number()) %>% # give it an index
  rename("Search Radius" = "Radius")  
  #mutate(`Search Radius` = fct_inorder(as.factor(`Search Radius`))) ## results in error for chunk starting on line 201

### getting better labels on the facet_grid
new_label_all_dat <- new_all_dat

new_label_all_dat$Radius <- factor(new_label_all_dat$`Search Radius`, levels =c("0.05", "0.10", "0.15"),
                                    labels = c("0.05", "0.10", "0.15"))

### have to create a new data set then pivot longer the average count 
new1 <- new_all_dat %>% 
  select(-c(Gitter, `Distance 1`, `Distance 2`, id, Confidence)) %>% 
  rename("layer_0" = `Highest Vote`) %>%
  rename("Layer_01_mean" = `Layer 1 mean`) %>% 
  rename("Layer_02_mean" = `Layer 2 mean`) %>% 
  rename("Layer_03_mean" = `Layer 3 mean`) %>% 
  rename("Layer_04_mean" = `Layer 4 mean`) %>% 
  rename("Layer_05_mean" = `Layer 5 mean`) %>% 
  rename("Layer_06_mean" = `Layer 6 mean`) %>% 
  rename("Layer_07_mean" = `Layer 7 mean`) %>% 
  rename("Layer_08_mean" = `Layer 8 mean`) %>% 
  rename("Layer_09_mean" = `Layer 9 mean`) %>% 
  rename("Layer_10_mean" = `Layer 10 mean`) %>% 
  rename("Layer_11_mean" = `Layer 11 mean`) %>% 
  rename("Layer_12_mean" = `Layer 12 mean`) %>% 
  rename("Layer_13_mean" = `Layer 13 mean`) %>% 
  rename("Layer_14_mean" = `Layer 14 mean`) %>% 
  rename("Layer_15_mean" = `Layer 15 mean`) %>% 
  rename("Layer_16_mean" = `Layer 16 mean`) %>% 
  rename("Layer_17_mean" = `Layer 17 mean`) %>% 
  rename("Layer_18_mean" = `Layer 18 mean`) %>% 
  rename("Layer_19_mean" = `Layer 19 mean`) %>% 
  rename("Layer_20_mean" = `Layer 20 mean`) %>% 
  pivot_longer(-c(`Search Radius`, Resolution, "test_circle"),
               names_to="Layer", 
               values_to = "Layer_Vote")
```


# Graphs {.tabset .tabset-fade .tabset-pills}

- NOTE THE CHANGE IN SCALE BETWEEN THE GRAPHS - SCALES MAY BE INDEPENDENT.

## Line Graphs

### Data from test circle of radius 0.05

```{r testRadius-0.05, echo=FALSE}
new_label_all_dat %>% 
  filter(test_circle == "Rad_0.05") %>%
  mutate(`Search Radius` = fct_inorder(as.factor(`Search Radius`))) %>% 
  ggplot(aes(group=Resolution)) +
  geom_point(aes(id, y=`Distance 1`), color="blue4") + 
  geom_line(aes(id, y=`Distance 1`), color="blue4") + 
  geom_point(aes(id, y=`Distance 2`)) + 
  geom_line(aes(id, y=`Distance 2`)) +
  facet_grid(`Search Radius`~Resolution,
             labeller=label_both, 
             scales = "free") + 
  labs(title = "Method 1 & 2 results from imperfect circle of radius 0.05", 
       subtitle = "Blue = Method 1",
       y = "Distance from dumd mean") +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), 
        axis.ticks.x = element_blank(),
        axis.title.y = element_text(size = 16))

```


### Data from test circle of radius 0.1

```{r testRadius-0.1, echo=FALSE}
new_label_all_dat %>% 
  filter(test_circle == "Rad_0.1") %>%
  mutate(`Search Radius` = fct_inorder(as.factor(`Search Radius`))) %>% 
  ggplot(aes(group=Resolution)) +
  geom_point(aes(id, y=`Distance 1`), color="blue4") + 
  geom_line(aes(id, y=`Distance 1`), color="blue4") + 
  geom_point(aes(id, y=`Distance 2`)) + 
  geom_line(aes(id, y=`Distance 2`)) +
  facet_grid(`Search Radius`~Resolution,
             labeller=label_both, 
             scales = "free") + 
  labs(title = "Method 1 & 2 results from imperfect circle of radius 0.1", 
       subtitle = "Blue = Method 1",
       y = "Distance from dumd mean") +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), 
        axis.ticks.x = element_blank(),
        axis.title.y = element_text(size = 16))
```


### Data from test circle of radius 0.15

```{r testRadius-0.15, echo=FALSE}
new_label_all_dat %>% 
  filter(test_circle == "Rad_0.15") %>%
  mutate(`Search Radius` = fct_inorder(as.factor(`Search Radius`))) %>% 
  ggplot(aes(group=Resolution)) +
  geom_point(aes(id, y=`Distance 1`), color="blue4") + 
  geom_line(aes(id, y=`Distance 1`), color="blue4") + 
  geom_point(aes(id, y=`Distance 2`)) + 
  geom_line(aes(id, y=`Distance 2`)) +
  facet_grid(`Search Radius`~Resolution,
             labeller=label_both, 
             scales = "free") + 
  labs(title = "Method 1 & 2 results from imperfect circle of radius 0.15", 
       subtitle = "Blue = Method 1",
       y = "Distance from dumd mean") +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), 
        axis.ticks.x = element_blank(),
        axis.title.y = element_text(size = 16))
```


## Distribution Graphs

### Distribution of method 1

```{r Distance 1 distribution, echo=FALSE}
new_all_dat %>% 
  ggplot(aes(fct_inorder(as.factor(`Search Radius`)), y=`Distance 1`, color=fct_inorder(as.factor(`Search Radius`)))) +
  geom_boxplot() + 
  geom_jitter() +
  labs(title = "Overall Distribution of Method 1 by Radius and Resolution", 
       x = "Search Radius") +
  facet_grid(~Resolution, labeller = label_both) +
  theme(legend.position = "none", 
        axis.title.y = element_text(size = 16), 
        axis.title.x = element_text(size = 16))
```


### Overall Distribution of method 1

```{r overall distribution, echo=FALSE}
### Overall distribution of method/Distance 1
new_all_dat %>% 
  ggplot(aes(fct_inorder(as.factor(`Search Radius`)), y=`Distance 1`, color=fct_inorder(as.factor(`Search Radius`)))) +
  geom_boxplot() + 
  geom_jitter() +
  labs(title = "Overall Distribution of Method 1 by Radius", 
       x = "Search Radius") +
  theme(legend.position = "none", 
        axis.title.y = element_text(size = 16), 
        axis.title.x = element_text(size = 16))
```


### Distribution of method 2

```{r Distance 2 distribution, echo=FALSE}
### distribution of method 2
new_all_dat %>% 
  ggplot(aes(fct_inorder(as.factor(`Search Radius`)), y=`Distance 2`, color=fct_inorder(as.factor(`Search Radius`)))) +
  geom_boxplot() + 
  geom_jitter() +
  labs(title = "Overall Distribution of Method 2 by Radius and Resolution", 
       x="Search Radius") +
  facet_grid(~Resolution, labeller = label_both) +
  theme(legend.position = "none", 
        axis.title.y = element_text(size = 16), 
        axis.title.x = element_text(size = 16))
```


### Overall Distribution of method 2

```{r overall distribution of method 2, echo=FALSE}
new_all_dat %>% 
  ggplot(aes(fct_inorder(as.factor(`Search Radius`)), y=`Distance 2`, color=fct_inorder(as.factor(`Search Radius`)))) +
  geom_boxplot() + 
  geom_jitter() +
  labs(title = "Overall Distribution of Method 2 by Radius", 
       x="Search Radius") +
  theme(legend.position = "none", 
        axis.title.y = element_text(size = 16), 
        axis.title.x = element_text(size = 16))
```


## Bar Graphs

### Overall Average Highest Votes

```{r overall, echo=FALSE}
## bar plot with position dodge showing the mean of highest vote 
# extracting the vote and rounding. 
new_test <- new_all_dat %>%
  group_by(`Search Radius`, Resolution) %>% 
  summarise(avg_high_vote = mean(`Highest Vote`)) %>% 
  round(., digits = 2) %>% 
  pull(avg_high_vote)
 
new_all_dat %>% 
  group_by(`Search Radius`, Resolution) %>% 
  summarise(avg_high_vote = mean(`Highest Vote`)) %>% 
  ggplot(aes(x=fct_inorder(as.factor(`Search Radius`)), y=avg_high_vote, fill=`Search Radius`)) +
  geom_col() +
  geom_text(aes(label=new_test), nudge_y = 1) +
  facet_grid(~Resolution, labeller = label_both) +
  labs(title = "Average Highest Vote by Radius and Resolution", 
       x = "Search Radius", 
       y = "Votes") +
  theme(legend.position = "position", 
        axis.title.y = element_text(size = 16), 
        axis.title.x = element_text(size = 16))
  #want to change color and order of Radius
```


### Average highest vote for test circle of 0.05

```{r avg high vote 0.05, echo=FALSE}
## bar plot with position dodge showing the mean of highest vote 
# extracting the vote and rounding.

#getting the proper numbers to label with  for test circle 0.01
test_5 <- new_all_dat %>%
  filter(test_circle == "Rad_0.05") %>% 
  group_by(`Search Radius`, Resolution) %>% 
  summarise(avg_high_vote = mean(`Highest Vote`)) %>% 
  round(., digits = 2) %>% 
  pull(avg_high_vote)
 
new_all_dat %>% 
  filter(test_circle == "Rad_0.05") %>% 
  group_by(`Search Radius`, Resolution) %>% 
  summarise(avg_high_vote = mean(`Highest Vote`)) %>% 
  ggplot(aes(x=fct_inorder(as.factor(`Search Radius`)), y=avg_high_vote, fill=`Search Radius`)) +
  geom_col() +
  geom_text(aes(label=test_5), nudge_y = 1) +
  facet_grid(~Resolution, labeller = label_both) +
  labs(title = "Average Highest Vote by Radius and Resolution", 
       x = "Search Radius", 
       y = "Votes") +
  theme(legend.position = "position", 
        axis.title.y = element_text(size = 16), 
        axis.title.x = element_text(size = 16))
  #want to change color and order of Radius
```


### Average highest vote for test circle of 0.1

```{r avg high vote 0.1, echo=FALSE}
## bar plot with position dodge showing the mean of highest vote 
# extracting the vote and rounding.

#getting the proper numbers to label with  for test circle 0.01
test_1 <- new_all_dat %>%
  filter(test_circle == "Rad_0.1") %>% 
  group_by(`Search Radius`, Resolution) %>% 
  summarise(avg_high_vote = mean(`Highest Vote`)) %>% 
  round(., digits = 2) %>% 
  pull(avg_high_vote)
 
new_all_dat %>% 
  filter(test_circle == "Rad_0.1") %>% 
  group_by(`Search Radius`, Resolution) %>% 
  summarise(avg_high_vote = mean(`Highest Vote`)) %>% 
  ggplot(aes(x=fct_inorder(as.factor(`Search Radius`)), y=avg_high_vote, fill=`Search Radius`)) +
  geom_col() +
  geom_text(aes(label=test_1), nudge_y = 1) +
  facet_grid(~Resolution, labeller = label_both) +
  labs(title = "Average Highest Vote by Radius and Resolution", 
       x = "Search Radius", 
       y = "Votes") +
  theme(legend.position = "position", 
        axis.title.y = element_text(size = 16), 
        axis.title.x = element_text(size = 16))
  #want to change color and order of Radius
```


### Average highest vote for test circle of 0.15

```{r avg high vote 0.15, echo=FALSE}
## bar plot with position dodge showing the mean of highest vote 
# extracting the vote and rounding.

#getting the proper numbers to label with  for test circle 0.01
test_15 <- new_all_dat %>%
  filter(test_circle == "Rad_0.15") %>% 
  group_by(`Search Radius`, Resolution) %>% 
  summarise(avg_high_vote = mean(`Highest Vote`)) %>% 
  round(., digits = 2) %>% 
  pull(avg_high_vote)
 
new_all_dat %>% 
  filter(test_circle == "Rad_0.15") %>% 
  group_by(`Search Radius`, Resolution) %>% 
  summarise(avg_high_vote = mean(`Highest Vote`)) %>% 
  ggplot(aes(x=fct_inorder(as.factor(`Search Radius`)), y=avg_high_vote, fill=`Search Radius`)) +
  geom_col() +
  geom_text(aes(label=test_15), nudge_y = 1) +
  facet_grid(~Resolution, labeller = label_both) +
  labs(title = "Average Highest Vote by Radius and Resolution", 
       x = "Search Radius", 
       y = "Votes") +
  theme(legend.position = "position", 
        axis.title.y = element_text(size = 16), 
        axis.title.x = element_text(size = 16))
  #want to change color and order of Radius
```



## Average Layer Mean

### Average Layer Vote

```{r avg layer mean, echo=FALSE}
new1 %>% 
  group_by(`Search Radius`, Resolution, test_circle, Layer) %>% 
  summarise(lay_avg = mean(Layer_Vote)) %>% 
  ggplot(aes(x=test_circle, y=lay_avg, group=Layer, fill=Layer))+
  geom_col(position ="dodge") + 
  facet_grid(`Search Radius`~Resolution, labeller = label_both, scales = "free") + 
  labs(title = "Average vote every box outside the highest vote",
       y="Average layer vote", 
       x="Test circle") +
  theme(axis.text.x = element_text(angle = 90), 
        axis.title.y = element_text(size = 16), 
        axis.title.x = element_text(size = 16))
```


### Average Confidence

#### Data from test circe of radius 0.05

```{r avg confindence g0.01 rad_0.05, echo=FALSE}
conf <- new_label_all_dat %>% 
  select(-c(4:26)) %>% 
  select(-c(Gitter, Radius, id)) %>%
  group_by(Resolution, `Search Radius`, test_circle) %>%
  summarise(conf_avg = mean(Confidence))

num_5 <- conf %>%
  filter(test_circle == "Rad_0.05") %>% 
  select(-c(`Search Radius`, Resolution, test_circle)) %>%
  round(., digits = 3) %>%
  pull(conf_avg)
  

new_label_all_dat %>% 
  filter(test_circle == "Rad_0.05") %>% 
  group_by(Resolution, `Search Radius`) %>%
  summarise(conf_avg = mean(Confidence)) %>% 
  mutate(`Search Radius` = fct_inorder(as.factor(`Search Radius`))) %>% 
  ggplot(aes(x=`Search Radius`, y=conf_avg, fill=`Search Radius`)) +
  geom_col() +
  geom_text(aes(label=num_5), nudge_y = 0.025) +
  facet_grid(~Resolution, labeller = label_both) + 
  labs(title = "Average confidence", 
       subtitle = "from 0 to 1", 
       x= "Search Radius", 
       y= "Average confidence") + 
  theme(legend.position = "none",
        axis.title.x = element_text(size = 16),
        axis.title.y = element_text(size = 16))

```

```{r confidence table, echo=FALSE}
# need to group by resolution and search radius to get the values for each one
## then create table like the facet wrap.
conf <- new_label_all_dat %>% 
  select(-c(4:26)) %>% 
  select(-c(Gitter, Radius, id)) %>%
  group_by(Resolution, `Search Radius`, test_circle) %>%
  summarise(conf_avg = mean(Confidence))

#not working
# conf_table <- conf %>% 
#   filter(test_circle == "Rad_0.05") %>%
#   select(-test_circle) #%>% 
#   # table(conf$Resolution, conf$`Search Radius`)
# 
# #use library(mosaic)
# table <- conf_table %>% 
#   round(., digits = 3) %>% 
#   matrix(nrow = 3, ncol = 3, byrow = TRUE, dimnames = c(Resolution, `Search Radius`))

conf_wider <- conf %>% 
  pivot_wider(names_from = Resolution, values_from=conf_avg)

datatable(conf_wider)


```


#### Data from test circe of radius 0.1

```{r avg confidence g0.01 rad_0.1, echo=FALSE}
num_1 <- conf %>%
  filter(test_circle == "Rad_0.1") %>% 
  select(-c(`Search Radius`, Resolution, test_circle)) %>%
  round(., digits = 3) %>%
  pull(conf_avg)

new_label_all_dat %>% 
  filter(test_circle == "Rad_0.1") %>% 
  group_by(Resolution, `Search Radius`) %>%
  summarise(conf_avg = mean(Confidence)) %>%
  mutate(`Search Radius` = fct_inorder(as.factor(`Search Radius`))) %>% 
  ggplot(aes(x=`Search Radius`, y=conf_avg, fill=`Search Radius`)) +
  geom_col() +
  geom_text(aes(label=num_1), nudge_y = 0.025) +
  facet_grid(~Resolution, labeller = label_both) +
  labs(title = "Average confidence", 
       subtitle = "from 0 to 1", 
       x= "Search Radius", 
       y= "Average confidence") + 
  theme(axis.title.x = element_text(size = 16),
        axis.title.y = element_text(size = 16))
```

#### Data from test circe of radius 0.15

```{r avg confidence g0.01 rad_0.15, echo=FALSE}
num_15 <- conf %>%
  filter(test_circle == "Rad_0.15") %>% 
  select(-c(`Search Radius`, Resolution, test_circle)) %>%
  round(., digits = 3) %>%
  pull(conf_avg)

new_label_all_dat %>% 
  filter(test_circle == "Rad_0.15") %>% 
  group_by(Resolution, `Search Radius`) %>%
  summarise(conf_avg = mean(Confidence)) %>%
  mutate(`Search Radius` = fct_inorder(as.factor(`Search Radius`))) %>% 
  ggplot(aes(x=`Search Radius`, y=conf_avg, fill=`Search Radius`)) +
  geom_col() +
  geom_text(aes(label=num_15), nudge_y = 0.025) +
  facet_grid(~Resolution, labeller = label_both) +
  labs(title = "Average confidence", 
       subtitle = "from 0 to 1", 
       x= "Search Radius", 
       y= "Average confidence") + 
  theme(axis.title.x = element_text(size = 16),
        axis.title.y = element_text(size = 16))
```